Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-02-09 manuscriptPLOSBIO_InitialSubmission.Rmd
Additional edits to PLOS submission

knitr::include_graphics(paste0(figdir,'blank.pdf'))

@@

knitr::include_graphics(paste0(figdir,'blank.pdf'))

@@

knitr::include_graphics(paste0(figdir,'blank.pdf'))

@@

knitr::include_graphics(paste0(figdir,'blank.pdf'))

@@

knitr::include_graphics(paste0(figdir,'blank.pdf'))

@@

knitr::include_graphics(paste0(figdir,'blank.pdf'))

>>>>

knitr::include_graphics(paste0(figdir,'pupildata.pdf'))

@@

knitr::include_graphics(paste0(figdir,'EEGdata.pdf'))

@@

knitr::include_graphics(paste0(figdir,'BSratios.pdf'))

@@

knitr::include_graphics(paste0(figdir,'TFdata.pdf'))

@@

knitr::include_graphics(paste0(figdir,'matchingdata.pdf'))

@@

knitr::include_graphics(paste0(figdir,'modelfigure.pdf'))
